Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-05-08 Paper.tex
EIP96: specify BLOCKHASH instruction during the first 256 blocks in Metropolis

>>>>

\section{Anomalies on the Main Network}

\subsection{Early behavior of BLOCKHASH instruction}
\label{sec:blockhash-early-metropolis}

During the first 256 blocks in the Metropolis phase, {\small BLOCKHASH} instruction behaves as specified below.

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
0x40 & {\small BLOCKHASH} & 1 & 1 & Get the hash of one of the 256 most recent complete blocks. \\
&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv P(I_{H_p}, \boldsymbol{\mu}_\mathbf{s}[0], 0)$ \\
&&&& where $P$ is the hash of a block of a particular number, up to a maximum age.\\
&&&& 0 is left on the stack if the looked for block number is greater than the current block number \\
&&&& or more than 256 blocks behind the current block. \\
&&&& $P(h, n, a) \equiv \begin{cases} 0 & \text{if} \quad n > H_i \vee a = 256 \vee h = 0 \\ h & \text{if} \quad n = H_i \\ P(H_p, n, a + 1) & \text{otherwise} \end{cases}$ \\
&&&& and we assert the header $H$ can be determined as its hash is the parent hash \\
&&&& in the block following it. \\
\bottomrule
\end{tabular*}
